<!--
|  (C) 2006-2024 Potsdam Institute for Climate Impact Research (PIK)
|  authors, and contributors see CITATION.cff file. This file is part
|  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
|  AGPL-3.0, you are granted additional permissions described in the
|  REMIND License Exception, version 1.0 (see LICENSE file).
|  Contact: remind@pik-potsdam.de
-->
# Air Pollutants for CMIP7 harmonization - REMIND-MAgPIE

```{r, echo = FALSE, results = 'hide'}
# Adds a new variable as the sum of a list of variables
addSumVariables <- function(
  fdata, sumvars, outvarname, outunit = NULL, convmult = 1, convoffset = 0, only.new = FALSE
  ) {
  if (is.null(outunit)) {
    outunit <- fdata %>%
      filter(variable == sumvars[1]) %>%
      slice(1) %>%
      select(unit) %>% unlist %>% as.character
  }

  newdata <- fdata %>%
    filter(variable %in% sumvars) %>%
    select(-varplus) %>%
    distinct %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(value = rowSums(across(sumvars))) %>%
    select(-c(sumvars)) %>%
    mutate(variable = outvarname, varplus = outvarname, unit = outunit)
  if(!only.new) {
    return(rbind(fdata, newdata))
  } else {
    return(newdata)
  }
}
```

```{r, echo = FALSE, results = 'hide'}

# Compute total emissions for CMIP7 harmonization sectors from REMIND
for (species in c("BC", "CO", "NH3", "NOX", "OC", "SO2", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|Extra|Energy|Demand|Transport|Pass|Aviation"),
    paste0("Emi|", species, "|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping"),
    paste0("Emi|", species, "|Energy Supply"),
    paste0("Emi|", species, "|Energy Demand|Industry"),
    paste0("Emi|", species, "|Energy Demand|Buildings"),
    paste0("Emi|", species, "|Solvents"),
    paste0("Emi|", species, "|Energy Demand|Transport"),
    paste0("Emi|", species, "|Waste")
  )
  
  data <- data %>% 
    filter(model == "REMIND") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|REMIND total"), only.new = TRUE) %>%
    bind_rows(data)
}

# Compute total emissions for CMIP7 harmonization sectors from MAgPIE
for (species_MAgPIE in c("BC", "CO", "NH3", "NO2", "OC", "SO2", "VOC")) {
  if (species_MAgPIE %in% c("NH3","NO2")) {
    sumvars <- c(
      paste0("Emissions|", species_MAgPIE, "|Land|Biomass Burning|Burning of Crop Residues"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Forest Burning"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Grassland Burning"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Peat Burning"),
      paste0("Emissions|", species_MAgPIE, "|Land|Agriculture")
    ) 
  }
  else {
    sumvars <- c(
      paste0("Emissions|", species_MAgPIE, "|Land|Biomass Burning|Burning of Crop Residues"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Forest Burning"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Grassland Burning"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Land|Fires|Peat Burning"),
      paste0("Emissions|", species_MAgPIE, "|AFOLU|Agriculture")
    ) 
  }

  data <- data %>% 
    filter(model == "MAgPIE") %>%
    addSumVariables(sumvars, paste0("Emissions|", species_MAgPIE,"|MAgPIE total"), only.new = TRUE) %>%
    bind_rows(data)
}


# Compute total emissions for CMIP7 harmonization sectors from REMIND and MAgPIE
for (species in c("BC", "CO", "NH3", "NOX", "OC", "SO2", "VOC")) {
  if (species == "NOX") {
    species_MAgPIE <- "NO2"
  } else {
    species_MAgPIE <- species
  }
  
  sumvars <- c(
    paste0("Emissions|", species_MAgPIE,"|MAgPIE total"), 
    paste0("Emi|", species,"|REMIND total")
  )
  
  data <- data %>% 
    filter(model %in% c("MAgPIE", "REMIND")) %>% mutate(model = "REMIND-MAgPIE", unit = "Mt NOX/yr") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|REMIND-MAgPIE total"), only.new = TRUE) %>%
    bind_rows(data)
}


# Compute total emissions for CMIP7 harmonization sectors from CEDS
for (species in c("BC", "CO", "NH3", "NOX", "OC", "Sulfur", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|Aircraft"),
    paste0("Emi|", species, "|International Shipping"),
    paste0("Emi|", species, "|Energy Sector"),
    paste0("Emi|", species, "|Industrial Sector"),
    paste0("Emi|", species, "|Residential Commercial Other"),
    paste0("Emi|", species, "|Solvents Production and Application"),
    paste0("Emi|", species, "|Transportation Sector"),
    paste0("Emi|", species, "|Waste")
  )
  
  data <- data %>% 
    filter(model == "CEDS IAMC sectors") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|REMIND total"), only.new = TRUE) %>%
    bind_rows(data)
}
```

## BC

### Emi|BC|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|BC|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|BC|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|BC|REMIND total", histVars = "Emi|BC|REMIND total", vlines = 2020)
```

### Emi|BC|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|BC|MAgPIE total", vlines = 2020)
```

### Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|BC|Aircraft", vlines = 2020)
```

### Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|BC|International Shipping", vlines = 2020)
```

### Emissions|BC|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|BC|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|BC|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|BC|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|BC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|BC|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|BC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|BC|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|BC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|BC|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|BC|AFOLU|Agriculture", vlines = 2020)
```

### Emi|BC|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|BC|Energy Supply", histVars = "Emi|BC|Energy Sector", vlines = 2020)
```

### Emi|BC|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|BC|Energy Demand|Industry", histVars = "Emi|BC|Industrial Sector", vlines = 2020)
```

### Emi|BC|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|BC|Energy Demand|Buildings", histVars = "Emi|BC|Residential Commercial Other", vlines = 2020)
```

### Emi|BC|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|BC|Solvents", histVars = "Emi|BC|Solvents Production and Application", vlines = 2020)
```

### Emi|BC|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|BC|Energy Demand|Transport", histVars = "Emi|BC|Transportation Sector", vlines = 2020)
```

### Emi|BC|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|BC|Waste", histVars = "Emi|BC|Waste", vlines = 2020)
```


## CO

### Emi|CO|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|CO|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|CO|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|CO|REMIND total", histVars = "Emi|CO|REMIND total", vlines = 2020)
```

### Emi|CO|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|CO|MAgPIE total", vlines = 2020)
```

### Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|CO|Aircraft", vlines = 2020)
```

### Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|CO|International Shipping", vlines = 2020)
```

### Emissions|CO|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|CO|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|CO|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|CO|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|CO|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|CO|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|CO|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|CO|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|CO|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|CO|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|CO|AFOLU|Agriculture", vlines = 2020)
```

### Emi|CO|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|CO|Energy Supply", histVars = "Emi|CO|Energy Sector", vlines = 2020)
```

### Emi|CO|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|CO|Energy Demand|Industry", histVars = "Emi|CO|Industrial Sector", vlines = 2020)
```

### Emi|CO|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|CO|Energy Demand|Buildings", histVars = "Emi|CO|Residential Commercial Other", vlines = 2020)
```

### Emi|CO|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|CO|Solvents", histVars = "Emi|CO|Solvents Production and Application", vlines = 2020)
```

### Emi|CO|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|CO|Energy Demand|Transport", histVars = "Emi|CO|Transportation Sector", vlines = 2020)
```

### Emi|CO|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|CO|Waste", histVars = "Emi|CO|Waste", vlines = 2020)
```


## NH3

### Emi|NH3|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|NH3|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|NH3|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|NH3|REMIND total", histVars = "Emi|NH3|REMIND total", vlines = 2020)
```

### Emi|NH3|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|NH3|MAgPIE total", vlines = 2020)
```

### Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NH3|Aircraft", vlines = 2020)
```

### Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NH3|International Shipping", vlines = 2020)
```

### Emissions|NH3|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|NH3|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|NH3|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|NH3|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|NH3|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|NH3|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|NH3|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|NH3|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|NH3|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|NH3|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|NH3|Land|Agriculture", vlines = 2020)
```

### Emi|NH3|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|NH3|Energy Supply", histVars = "Emi|NH3|Energy Sector", vlines = 2020)
```

### Emi|NH3|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|NH3|Energy Demand|Industry", histVars = "Emi|NH3|Industrial Sector", vlines = 2020)
```

### Emi|NH3|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|NH3|Energy Demand|Buildings", histVars = "Emi|NH3|Residential Commercial Other", vlines = 2020)
```

### Emi|NH3|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|NH3|Solvents", histVars = "Emi|NH3|Solvents Production and Application", vlines = 2020)
```

### Emi|NH3|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|NH3|Energy Demand|Transport", histVars = "Emi|NH3|Transportation Sector", vlines = 2020)
```

### Emi|NH3|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|NH3|Waste", histVars = "Emi|NH3|Waste", vlines = 2020)
```


## NOX

### Emi|NOX|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|NOX|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|NOX|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|NOX|REMIND total", histVars = "Emi|NOX|REMIND total", vlines = 2020)
```

### Emi|NO2|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|NO2|MAgPIE total", vlines = 2020)
```

### Emi|NOX|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|NOX|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NOX|Aircraft", vlines = 2020)
```

### Emi|NOX|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|NOX|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NOX|International Shipping", vlines = 2020)
```

### Emissions|NO2|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|NO2|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|NO2|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|NO2|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|NO2|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|NO2|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|NO2|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|NO2|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|NO2|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|NO2|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|NO2|Land|Agriculture", vlines = 2020)
```

### Emi|NOX|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|NOX|Energy Supply", histVars = "Emi|NOX|Energy Sector", vlines = 2020)
```

### Emi|NOX|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|NOX|Energy Demand|Industry", histVars = "Emi|NOX|Industrial Sector", vlines = 2020)
```

### Emi|NOX|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|NOX|Energy Demand|Buildings", histVars = "Emi|NOX|Residential Commercial Other", vlines = 2020)
```

### Emi|NOX|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|NOX|Solvents", histVars = "Emi|NOX|Solvents Production and Application", vlines = 2020)
```

### Emi|NOX|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|NOX|Energy Demand|Transport", histVars = "Emi|NOX|Transportation Sector", vlines = 2020)
```

### Emi|NOX|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|NOX|Waste", histVars = "Emi|NOX|Waste", vlines = 2020)
```



## OC

### Emi|OC|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|OC|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|OC|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|OC|REMIND total", histVars = "Emi|OC|REMIND total", vlines = 2020)
```

### Emi|OC|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|OC|MAgPIE total", vlines = 2020)
```

### Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|OC|Aircraft", vlines = 2020)
```

### Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|OC|International Shipping", vlines = 2020)
```

### Emissions|OC|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|OC|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|OC|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|OC|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|OC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|OC|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|OC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|OC|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|OC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|OC|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|OC|AFOLU|Agriculture", vlines = 2020)
```

### Emi|OC|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|OC|Energy Supply", histVars = "Emi|OC|Energy Sector", vlines = 2020)
```

### Emi|OC|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|OC|Energy Demand|Industry", histVars = "Emi|OC|Industrial Sector", vlines = 2020)
```

### Emi|OC|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|OC|Energy Demand|Buildings", histVars = "Emi|OC|Residential Commercial Other", vlines = 2020)
```

### Emi|OC|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|OC|Solvents", histVars = "Emi|OC|Solvents Production and Application", vlines = 2020)
```

### Emi|OC|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|OC|Energy Demand|Transport", histVars = "Emi|OC|Transportation Sector", vlines = 2020)
```

### Emi|OC|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|OC|Waste", histVars = "Emi|OC|Waste", vlines = 2020)
```


## SO2

### Emi|SO2|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|SO2|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|SO2|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|SO2|REMIND total", histVars = "Emi|Sulfur|REMIND total", vlines = 2020)
```

### Emi|SO2|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|SO2|MAgPIE total", vlines = 2020)
```

### Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|Sulfur|Aircraft", vlines = 2020)
```

### Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|Sulfur|International Shipping", vlines = 2020)
```

### Emissions|SO2|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|SO2|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|Sulfur|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|SO2|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|SO2|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|SO2|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|SO2|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|SO2|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|SO2|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|SO2|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|SO2|AFOLU|Agriculture", vlines = 2020)
```

### Emi|SO2|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|SO2|Energy Supply", histVars = "Emi|Sulfur|Energy Sector", vlines = 2020)
```

### Emi|SO2|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|SO2|Energy Demand|Industry", histVars = "Emi|Sulfur|Industrial Sector", vlines = 2020)
```

### Emi|SO2|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|SO2|Energy Demand|Buildings", histVars = "Emi|Sulfur|Residential Commercial Other", vlines = 2020)
```

### Emi|SO2|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|SO2|Solvents", histVars = "Emi|Sulfur|Solvents Production and Application", vlines = 2020)
```

### Emi|SO2|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|SO2|Energy Demand|Transport", histVars = "Emi|Sulfur|Transportation Sector", vlines = 2020)
```

### Emi|SO2|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|SO2|Waste", histVars = "Emi|Sulfur|Waste", vlines = 2020)
```


## VOC

### Emi|VOC|REMIND-MAgPIE total
```{r Black Carbon Emissions - REMIND-MAgPIE Total}
showLinePlots(data, "Emi|VOC|REMIND-MAgPIE total", vlines = 2020)
```

### Emi|VOC|REMIND total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emi|VOC|REMIND total", histVars = "Emi|VOC|REMIND total", vlines = 2020)
```

### Emi|VOC|MAgPIE total
```{r Black Carbon Emissions - REMIND Total}
showLinePlots(data, "Emissions|VOC|MAgPIE total", vlines = 2020)
```

### Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|VOC|Aircraft", vlines = 2020)
```

### Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r Black Carbon Emissions - Total}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|VOC|International Shipping", vlines = 2020)
```

### Emissions|VOC|Land|Biomass Burning|Burning of Crop Residues
```{r Black Carbon Emissions - Biomass Burning}
showLinePlots(data, "Emissions|VOC|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emissions|VOC|Land|Biomass Burning|+|Agricultural Waste Burning", vlines = 2020)
```

### Emissions|VOC|AFOLU|Land|Fires|Forest Burning
```{r Black Carbon Emissions - Forest Burning}
showLinePlots(data, "Emissions|VOC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emissions|VOC|AFOLU|Land|Fires|Grassland Burning
```{r Black Carbon Emissions - Grassland Burning}
showLinePlots(data, "Emissions|VOC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emissions|VOC|AFOLU|Land|Fires|Peat Burning
```{r Black Carbon Emissions - Peat Burning}
showLinePlots(data, "Emissions|VOC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

### Emissions|VOC|AFOLU|Agriculture
```{r Black Carbon Emissions - Agriculture}
showLinePlots(data, "Emissions|VOC|AFOLU|Agriculture", vlines = 2020)
```

### Emi|VOC|Energy Supply
```{r Black Carbon Emissions - Energy Supply}
showLinePlots(data, "Emi|VOC|Energy Supply", histVars = "Emi|VOC|Energy Sector", vlines = 2020)
```

### Emi|VOC|Energy Demand|Industry
```{r Black Carbon Emissions - Industry}
showLinePlots(data, "Emi|VOC|Energy Demand|Industry", histVars = "Emi|VOC|Industrial Sector", vlines = 2020)
```

### Emi|VOC|Energy Demand|Buildings
```{r Black Carbon Emissions - Buildings}
showLinePlots(data, "Emi|VOC|Energy Demand|Buildings", histVars = "Emi|VOC|Residential Commercial Other", vlines = 2020)
```

### Emi|VOC|Solvents
```{r Black Carbon Emissions - Solvents}
showLinePlots(data, "Emi|VOC|Solvents", histVars = "Emi|VOC|Solvents Production and Application", vlines = 2020)
```

### Emi|VOC|Energy Demand|Transport
```{r Black Carbon Emissions - Transport}
showLinePlots(data, "Emi|VOC|Energy Demand|Transport", histVars = "Emi|VOC|Transportation Sector", vlines = 2020)
```

### Emi|VOC|Waste
```{r Black Carbon Emissions - Waste}
showLinePlots(data, "Emi|VOC|Waste", histVars = "Emi|VOC|Waste", vlines = 2020)
```
