---
title: "Transport decarbonization pathways in Europe"
author: ""
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
runtime: flexdashboard
---



```{r loading_required_libraries, include=FALSE}
  #Loading required libraries
  library(flexdashboard)
  library(ggplot2)
  library(plotly)
  library(magclass)
  library(mip)
  library(data.table)
```



```{r creating_charts, include=FALSE}
source("helper_dashboard.R")

legend=plotlist$legend

```

```{r global_options, include=FALSE}
  # setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svg', fig.asp = 1 ) # fig.asp = default aspect ratio
```

```{r creating_info_tooltips, include=FALSE}
  #data frame with help tooltips

  helpTooltip_df <- data.frame(
    title=c("Per capita Passenger Transport Energy Services Demand", "Total Passenger Transport Energy Services Demand", "Sales composition", "Final energy LDVs by fuel","Transport Passenger Final Energy Demand", "Fleet composition", "Fleet composition comparison", "Emission intensity, new sales comparison", "Comparison of passenger final energy demand"),
    placement=c("right", "left", "right", "left", "left", "left", "right", "left", "left"))


helpTooltip = function(tooltipdf){
  
  title <- as.character(tooltipdf$title) 
  placement <- as.character(tooltipdf$placement) 
  
  contents <- gsub('\n', '',gsub('"', '&quot;',paste0('
<div class="tooltipContainer">
  <div class="tooltipDescription">',
    legend[[title]]$description,'
  </div>
  <div class="legendContainer">
  	<table class="legendTable">
  		<tbody>
  			<tr>',
	      do.call(paste,lapply(names(legend[[title]]$contents),function(x){
        paste0('<tr><td>',
          ifelse(is.null(legend[[title]]$contents[[x]]$linetype),
                  paste0('<div class="square"><div class="circle" style="background-color:',legend[[title]]$contents[[x]]$fill,';"></div></div>'),
  				        paste0('<div class="line" style="border-color:',legend[[title]]$contents[[x]]$fill,'; border-style: ',legend[[title]]$contents[[x]]$linetype,';"></div>')
  				        ),'
            </td><td class="legendText">',x,'</td></tr>'
           )
  	    })),'
  		</tbody>
  	</table>
  </div>
</div>')))
  
  result = ""
  result = paste0(result,"<script type='text/javascript'>\n");
  result = paste0(result,"$(window).load(function () {\n");
  result = paste0(result,"  $('.chart-title').filter(function() { return $(this).clone().children().remove().end().text() == '", title, "' }).each(function(){\n");
  if(!(placement == "none"))
    result = paste0(result,"  	$(this).append('<i class=\"glyphicon glyphicon-info-sign infoIcon\" data-toggle=\"tooltip\" data-html=\"true\" data-placement=\"right\" title=\"",contents,"\"></i>');\n");
  result = paste0(result,"  	$(this).find('[data-toggle=\"tooltip\"]').tooltip({ placement:'",placement,"'});\n");
  result = paste0(result,"	})\n");
  result = paste0(result,"})\n");
  result = paste0(result,"</script>");

  return(result)
}

```

<!--############################# -->
<!--#### START OF MENUS CODE #### -->
<!--############################# -->

<!-- ### Creating main emissions menu ### -->

<!--Creating First Page - LDV Page-->
Overview {data-icon="glyphicon glyphicon-scale"}
===================================== 
Side Navigation {.sidebar .sidebarOverview data-width=60}
-------------------------------------

[](#overview){class="fas fa-thermometer-three-quarters sidebar-button selected"}
[](#overview-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case NoTax", icon = "fa-thermometer-three-quarters")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$`ConvCase NoTax`$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$`ConvCase NoTax`$plot$ESmodecap_pass
```

### Total Passenger Transport Energy Services Demand
```{r}
plotlist$`ConvCase NoTax`$plot$ESmodeabs
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Passenger Final Energy Demand

```{r}
plotlist$`ConvCase NoTax`$plot$EJpassfuels
```

### Emissions passenger transport demand

```{r}
plotlist$`ConvCase NoTax`$plot$emipdem
```

Overview Conv scenario {.hidden data-icon="glyphicon glyphicon-tint"}
===================================== 

Side Navigation {.sidebar .sidebarOverview data-width=60}
-------------------------------------

[](#overview){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#overview-conv-scenario){class="glyphicon glyphicon-oil sidebar-button selected"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case", icon = "glyphicon-oil")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ConvCase$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$ConvCase$plot$ESmodecap_pass
```

### Total Passenger Transport Energy Services Demand
```{r}
plotlist$ConvCase$plot$ESmodeabs
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Passenger Final Energy Demand

```{r}
plotlist$ConvCase$plot$EJpassfuels
```

### Emissions passenger transport demand

```{r}
plotlist$ConvCase$plot$emipdem
```


Overview FCEV scenario {.hidden data-icon="glyphicon glyphicon-tint"}
===================================== 

Side Navigation {.sidebar .sidebarOverview data-width=60}
-------------------------------------

[](#overview){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#overview-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button selected"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Hydrogen Hype", icon = "glyphicon-tint")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$HydrHype$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Hydrogen vehicles gain an important share of the mix thanks to policies oriented at promoting them.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$HydrHype$plot$ESmodecap_pass
```

### Total Passenger Transport Energy Services Demand
```{r}
plotlist$HydrHype$plot$ESmodeabs
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Passenger Final Energy Demand

```{r}
plotlist$HydrHype$plot$EJpassfuels
```

### Emissions passenger transport demand

```{r}
plotlist$HydrHype$plot$emipdem
```

Overview BEV scenario { .hidden data-icon="glyphicon glyphicon-flash"}
===================================== 

Side Navigation {.sidebar .sidebarOverview data-width=60}
-------------------------------------

[](#overview){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#overview-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button selected"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Electric Era", icon = "glyphicon-flash")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ElecEra$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Electric vehicles gain an important share of the mix thanks to policies oriented at promoting them.


<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$ElecEra$plot$ESmodecap_pass
```

### Total Passenger Transport Energy Services Demand
```{r}
plotlist$ElecEra$plot$ESmodeabs
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Passenger Final Energy Demand

```{r}
plotlist$ElecEra$plot$EJpassfuels
```

### Emissions passenger transport demand

```{r}
plotlist$ElecEra$plot$emipdem
```

Overview Synfuel scenario {.hidden data-icon="glyphicon glyphicon-random"}
===================================== 

Side Navigation {.sidebar .sidebarOverview data-width=60}
-------------------------------------

[](#overview){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#overview-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button selected"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Synfuel Surge", icon = "glyphicon-random")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$SynSurge$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Synthetic fuels gain great importance in the liquid fuels production. Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$SynSurge$plot$ESmodecap_pass
```

### Total Passenger Transport Energy Services Demand
```{r}
plotlist$SynSurge$plot$ESmodeabs
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Passenger Final Energy Demand

```{r}
plotlist$SynSurge$plot$EJpassfuels
```

### Emissions passenger transport demand

```{r}
plotlist$SynSurge$plot$emipdem
```


LDVs {data-icon="fa-car"}
===================================== 

Side Navigation {.sidebar .sidebarLDV data-width=60}
-------------------------------------

[](#ldvs){class="fas fa-thermometer-three-quarters sidebar-button selected"}
[](#ldvs-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case NoTax", icon = "fa-thermometer-three-quarters")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$`ConvCase NoTax`$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.

<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$`ConvCase NoTax`$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$`ConvCase NoTax`$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$`ConvCase NoTax`$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$`ConvCase NoTax`$plot$vintcomp
```

LDVs Conv scenario { .hidden data-icon="glyphicon glyphicon-flash"}
===================================== 

Side Navigation {.sidebar .sidebarLDV data-width=60}
-------------------------------------

[](#ldvs){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#ldvs-conv-scenario){class="glyphicon glyphicon-oil sidebar-button selected"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case", icon = "glyphicon-oil")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ConvCase$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.

<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$ConvCase$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$ConvCase$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$ConvCase$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$ConvCase$plot$vintcomp
```


LDVs FCEV scenario {.hidden data-icon="glyphicon glyphicon-tint"}
===================================== 

Side Navigation {.sidebar .sidebarLDV data-width=60}
-------------------------------------

[](#ldvs){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#ldvs-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button selected"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Hydrogen Hype", icon = "glyphicon-tint")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$HydrHype$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Hydrogen vehicles gain an important share of the mix thanks to policies oriented at promoting them.


<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$HydrHype$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$HydrHype$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$HydrHype$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$HydrHype$plot$vintcomp
```


LDVs BEV scenario { .hidden data-icon="glyphicon glyphicon-flash"}
===================================== 


Side Navigation {.sidebar .sidebarLDV data-width=60}
-------------------------------------

[](#ldvs){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#ldvs-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button selected"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Electric Era", icon = "glyphicon-flash")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ElecEra$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Electric vehicles gain an important share of the mix thanks to policies oriented at promoting them.


<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$ElecEra$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$ElecEra$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$ElecEra$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$ElecEra$plot$vintcomp
```


LDVs Synfuel scenario {.hidden data-icon="glyphicon glyphicon-random"}
===================================== 

Side Navigation {.sidebar .sidebarLDV data-width=60}
-------------------------------------

[](#ldvs){class="fas fa-thermometer-three-quarters sidebar-button"}
[](#ldvs-conv-scenario){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button selected"}

<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Synfuel Surge", icon = "glyphicon-random")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$SynSurge$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Synthetic fuels gain great importance in the liquid fuels production. Absence of policies oriented to promote alternative vehicles. Internal combustion engines lead the market.



<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$SynSurge$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$SynSurge$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$SynSurge$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$SynSurge$plot$vintcomp
```

Comparison {data-icon="fa-exchange-alt"}
=====================================
Row {data-height=300}
-----------------------------------------------------------------------

### Fleet composition comparison
```{r}
plotlist$comparison$plot$vintscen
```

### Emission intensity, new sales comparison
```{r}
plotlist$comparison$plot$CO2km_intensity_newsales_scen
```
Row {data-height=300}
-----------------------------------------------------------------------

### Comparison of passenger final energy demand
```{r}
plotlist$comparison$plot$EJpassfuels_scen
```

Assumptions {data-icon="fa-comment"}
=====================================

Column {data-width= 450}
-----------------------------------------------------------------------

### Conventional Case {data-height=200}

* Conventional consumers patterns
* No policies to promote alternative vehicles
* Learning rate on BEVs and FCEVs
* Market-driven behavior of light duty vehicles powertrain choice

### Hydrogen Hype {data-height=200}

* Learning rate on BEVs and FCEVs
* Optimistic trend of hydrogen refuelling stations
* Rebates-feebates scheme: 5000 ? subsidies starting in 2020 on FCEVs, phasing out by 2035. 1000 ? mark-up cost on internal combustion engines
* Market-driven behavior of light duty vehicles powertrain choice
* Policy push of FCEVs
* Hydrogen from renewable resources (green hydrogen) is set to be above 95\% of the total hydrogen

### Electric Era {data-height=200}

* Learning rate on BEVs and FCEVs
* Rebates-feebates scheme: 5000 ? subsidies starting in 2020 on BEVs, phasing out by 2035. 1000 ? mark-up cost on internal combustion engines
* Market-driven behavior of light duty vehicles powertrain choice

### Synfuel Surge {data-height=200}

* Conventional consumers patterns
* Learning rate on BEVs and FCEVs
* Market-driven behavior of light duty vehicles powertrain choice
* Synfuels are forced in the liquids mix reaching 10\% in 2035
* Hydrogen from renewable resources (green hydrogen) is set to be above 95% of the total hydrogen


<!-- creating information tooltip -->
```{r, results='asis'}
for(i in 1:nrow(helpTooltip_df)){
  cat(helpTooltip(helpTooltip_df[i,]))
}
```

<!-- #### additional html, js and CSS #### -->

<!-- js -->

<script type="text/javascript">
  var is_chrome = (typeof window.chrome === "object" && navigator.appVersion.indexOf('Edge') === -1);
</script>


<!-- Adding js function to add "memory" to the nav bar navigation   -->
```{r}
navBarMemory = function(topMenuLabel, sideBarClass){
  result = ""
  result = paste0(result,"<script type='text/javascript'>\n");
  result = paste0(result,"$(document).ready(function () {\n");
  result = paste0(result,"	$(\"",sideBarClass," a\").click(function(){\n");
  result = paste0(result,"	console.log($(this).attr('href'));\n");  
  result = paste0(result,"	console.log($(\".nav.navbar-nav.navbar-left a:contains('",topMenuLabel,"')\").attr('href'));\n"); 
  result = paste0(result,"	  $(\".nav.navbar-nav.navbar-left a:contains('",topMenuLabel,"')\").attr('href', $(this).attr('href'));\n");
  result = paste0(result,"	  if(!is_chrome){\n");
  result = paste0(result,"	    window.FlexDashboardUtils.showPage($(this).attr('href'));\n");
  result = paste0(result,"	  }\n"); 
  result = paste0(result,"	})\n");
  result = paste0(result,"})\n");
  result = paste0(result,"</script>");
  return(result)
}
```

```{r, results='asis'}
  cat(navBarMemory("Overview",".sidebarOverview"))
  cat(navBarMemory("LDVs",".sidebarLDV"))
```

<!-- ADVANCED: using CSS to define the appearance of the side bar --> 

<!-- CSS -->
<style type="text/css">

  .sidebar-button {  /* sidebar size  */
     display: inline-block;
     font-size: 40px;
     height: 80px;
     padding-top: 20px
  }
  
  .sidebar-button, .sidebar-button:hover {
    text-decoration: none;
  }
  
  .sidebar-button.selected, .sidebar-button.selected:hover {
    opacity: 1;
  }
  
  .sidebar-button {
    opacity: 0.7;
  }
  
  .sidebar-button:hover {
    opacity: 0.4;
  }
  
  /*legend*/
  .tooltipContainer {
    padding: 5px;
  }
  
  .tooltipDescription {
    width: fit-content;
    margin: 5px auto;
  }
  
  .legendContainer {
	}

  .legendTable {
    margin:auto;
    text-align: left;
    border-collapse: separate;
    border-spacing: 2px;
	}

  .legendText {
    padding: 4px 20px;
  }

  .legendTable tr:nth-child(odd) {
	  background-color: #1d1e1f; /* Background-color of odd rows */
  }

  .legendTable tr:nth-child(even) {
	  background-color: #32353a; /* Background-color of even rows */
  }

  .square {
    height: 16px; 
    width: 16px; 
    margin: 4px 12px;
  }

  .circle {
    height: 100%; 
    width: 100%; 
    border-radius: 50%; 
    display: inline-block;
  }
  
  .line{
    width: 80%; 
    min-width: 22px;
    border: 1px solid #fff;
    margin: auto;
  }
  
  .units {
    float: right;
    margin: -2px 5px 0 5px;
    color: #b7b7b7;
  }
  
  .infoIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .modalIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .expandIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .modalIcon:hover, .infoIcon:hover, .expandIcon:hover {
    color: #7c7c7c;
  }
  
  .unselectable {
    -webkit-touch-callout: none;
    -webkit-user-select: none;
    -khtml-user-select: none;
    -moz-user-select: none;
    -ms-user-select: none;
    user-select: none;
  }

</style>





