# |  (C) 2006-2020 Potsdam Institute for Climate Impact Research (PIK)
# |  authors, and contributors see CITATION.cff file. This file is part
# |  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
# |  AGPL-3.0, you are granted additional permissions described in the
# |  REMIND License Exception, version 1.0 (see LICENSE file).
# |  Contact: remind@pik-potsdam.de
---
title: "Compare scenarios Transport"
output:
  pdf_document: default
  html_document:
    df_print: paged
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = 'pdf')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
require(ggplot2)
require(moinput)
require(rmndt)
require(quitte)
library(lucode2)
library(magpie)
library(quitte)
library(cowplot)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Set RDS files path
EJmode_all = readRDS("EJmode_all.RDS")
EJroad_all = readRDS("EJroad_all.RDS")
fleet_all = readRDS("fleet_all.RDS")
salescomp_all = readRDS("salescomp_all.RDS")
ESmodecap_all = readRDS("ESmodecap_all.RDS")
CO2km_int_newsales_all = readRDS("CO2km_int_newsales_all.RDS")
EJpass_all = readRDS("EJfuelsPass_all.RDS")
EJfrgt_all = readRDS("EJfuelsFrgt_all.RDS")
emidem_all = readRDS("emidem_all.RDS")
elecdem_all = readRDS("elecdem_all.RDS")
costs_all = readRDS("costs_all.RDS")
pref_FV_all = readRDS("pref_FV_all.RDS")
dempkm_cap_all = readRDS("demgdpcap_all.RDS")

setConfig(forcecache=T)

cols <- c("NG" = "#d11141",
          "Gases" = "#d11141",
          "Coal" = "#113245",
          "Hydro" = "#87cefa",
          "Solar" = "#edae49",
          "Geothermal" = "#58b4ae",
          "Uranium" = "orchid",
          "Wind" = "#e43f5a",
          "Liquids" = "#8c8c8c",
          "Hybrid Liquids" = "#ffc425",
          "Hybrid Electric" = "#f37735",
          "BEV" = "#00b159",
          "Electricity" = "#00b159",
          "Electric" = "#00b159",
          "FCEV" = "#00aedb",
          "Hydrogen" = "#00aedb",
          "Biodiesel" = "#66a182",
          "Biomass" = "#66a182",
          "Synfuel" = "orchid",
          "Synfuels" = "orchid",
          "Oil" = "#2e4057",
          "O&M" = "#edae49",
          "Range anxiety" = "#e43f5a",
          "Refuel availability" = "#f79071",
          "Purchase" = "#d1495b",
          "Model availability" = "#58b4ae",
          "Inconvenience" = "#58b4ae",
          "Charging" = "#007892",
          "Policy induced inconvenience" = "#2e4057",
          "Risk" = "#feb72b",
          "Fuel" = "#035aa6",
          "International Aviation" = "#9acd32",
          "Domestic Aviation" = "#7cfc00",
          "Bus" = "#32cd32",
          "Passenger Rail" = "#2e8b57",
          "Freight Rail" = "#ee4000",
          "Trucks" = "#ff6a6a",
          "International Shipping" = "#cd2626",
          "Domestic Shipping" = "#ff4040",
          "Shipping" = "#ff4040",
          "Truck" = "#ff7f50",
          "Trucks (<3.5t)" = "#ff7f50",
          "Trucks (3.5t-16)" = "#8b0000",
          "Trucks (>16)" = "#fa8072",
          "Motorbikes" = "#1874cd",
          "Small Cars" = "#87cefa",
          "Large Cars" = "#6495ed",
          "Van" = " 	#40e0d0",
          "LDV" = "#00bfff",
          "Non motorized" = "#da70d6",
          "Freight"="#ff0000",
          "Freight (Inland)" = "#cd5555",
          "Pass non LDV" = "#6b8e23",
          "Pass" = "#66cdaa",
          "Pass non LDV (Domestic)" = "#54ff9f",
          "refined liquids enduse" = "#8c8c8c",
          "FE|Transport|Hydrogen" = "#00aedb",
          "FE|Transport|NG" = "#d11141",
          "FE|Transport|Liquids" = "#8c8c8c",
          "FE|Transport|Electricity" = "#00b159",
          "FE|Transport" = "#1e90ff",
          "FE|Buildings" = "#d2b48c",
          "FE|Industry" = "#919191",
          "ElecEra" = "#00b159",
          "ElecEraWise" = "#68c6a4",
          "HydrHype" = "#00aedb",
          "HydrHypeWise" = "#o3878f",
          "ConvCase" = "#113245",
          "ConvCaseWise" = "#d11141",
          "NDC" = "#d11141",
          "NPi_IC" = "#f6ab6c",
          "Budg_BE" = "#00b159",
          "Budg_IC" = "#113245",
          "Budg_ICsyn" = "orchid",
          "Budg_FC" = "#00aedb",
          "Budg_BE-LS" = "#68c6a4",
          "Budg_IC-LS" = "#d11141",
          "SynSurge" = "orchid")

legend_ord_modes <- c("Freight Rail", "Truck", "Shipping", "International Shipping", "Domestic Shipping",  "Trucks",
                "Motorbikes", "Small Cars", "Large Cars", "Van",
                "International Aviation", "Domestic Aviation","Bus", "Passenger Rail",
                "Freight", "LDV", "Pass non LDV", "Freight (Inland)", "Pass non LDV (Domestic)", "Non motorized")

legend_ord_fuels <- c("BEV", "Electricity", "Hybrid Electric", "FCEV", "Hydrogen", "Hybrid Liquids", "Liquids", "Oil", "Biodiesel", "Synfuel", "Synfuels", "Gases","NG")

legend_ord_costs <- c("Inconvenience", "Risk", "Charging", "Model availability", "Range anxiety", "Refuel availability", "Policy induced inconvenience","Fuel", "Purchase", "O&M")

legend_ord_emissions <- c("Emi|CO2|Industry|Gross", "Emi|CO2|Buildings|Direct", "Emi|CO2|Transport|Demand", "Emi|CO2|Energy|Supply|Gross", "Emi|CO2|Land-Use Change","Emi|CO2|CDR|BECCS")

legend_ord = c(legend_ord_modes, legend_ord_fuels, legend_ord_costs)

## mapping for scenario names
mapping_scens = data.table(scenario = c("Budg1100_ConvCase", "Budg1100_ElecEra", "Budg1100_HydrHype", "Budg1100_SynSurge", "NDC_ConvCase", "NPi", "Budg1100_ConvCaseWise", "Budg1100_ElecEraWise", "Budg1100_HydrHypeWise", "Budg1100_SynSurgeWise", "NDC_ConvCaseWise"), scen_name = c("ConvCase", "ElecEra", "HydrHype", "SynSurge", "NDC", "NPi", "ConvCaseWise", "ElecEraWise", "HydrHypeWise", "SynSurgeWise", "NDCWise"))

mapping_scens_paper = data.table(scenario = c("Budg1100_ConvCase", "Budg1100_ElecEra", "Budg1100_HydrHype", "Budg1100_SynSurge", "NDC_ConvCase", "NPi_ConvCase", "Budg1100_ConvCaseWise", "Budg1100_ElecEraWise"), scen_name = c("Budg_IC", "Budg_BE", "Budg_FC", "Budg_ICsyn", "NDC_IC", "NPi_IC", "Budg_IC-LS", "Budg_BE-LS"))


regionplot = "EUR"

## set the theme for the plots
theme2use <- theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, size=14, vjust=0.5, hjust=1),
          axis.text.y = element_text(size=14),
          axis.title.y = element_text(size=14),
          title = element_text(size=14),
          axis.line = element_line(size = 0.5, colour = "grey"),
          legend.text = element_text(size=14),
          strip.text = element_text(size=14),
          strip.background = element_rect(color = "grey"))
```


## Vintages by powertrain

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## Vintages
vintcomparisonpf = function(dt){
  dt = dt[year %in% c(2015, 2050, 2100)]
  plot = ggplot()+
    geom_bar(data = dt,
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, width=.75), alpha = 0.5, position="stack", stat = "identity", width = 0.5)+
    geom_bar(data = dt,
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, alpha = factor(alphaval),  width=.75), position="stack", stat = "identity", width = 0.5, color = "black", size=0.05)+
    guides(fill = guide_legend(reverse=TRUE))+
    facet_grid(year~region) +
    theme2use +
    scale_alpha_discrete(breaks = c(1,0), name = "Status", labels = c("Vintages","New additions")) +
    guides(linetype=FALSE,
           fill=guide_legend(reverse=FALSE, title="Transport mode"))+
    scale_fill_manual(values = cols)+
    labs(y = "[million Veh]", x="", title = "LDV fleet")
    return(plot)
}

vintcomparisonpf(fleet_all)

```

## Fleet total

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## Vintages as line plot, useful to compare the totals (e.g. normal VS WiseWays)

vintcomparisontotpf = function(dt, rp){
    dt = dt[,.(value = sum(value)), by = .(region, scenario, year)]

    dt[, type := ifelse(grepl("Wise",scenario), "WiseWays", "UsualUse"), by = c("region", "year", "scenario")]
    dt[, scenario := ifelse(grepl("NDC", scenario), "NDC", scenario)]
    dt[, scenario := gsub(".*_", "", scenario)]
    dt[, scenario := gsub("Wise", "", scenario)]

    plot_all = ggplot()+
    geom_line(data = dt,
             aes(x=year, y=value, group = interaction(scenario, type),
                 color = scenario, linetype = type))+
    facet_wrap(~region)+
    theme2use +
    labs(y = "[million Veh]", x="", title = "LDV fleet")+
      scale_color_manual("Scenario", values = cols)


    plot_reg = ggplot()+
    geom_line(data = dt[region == rp & year <= 2050],
             aes(x=year, y=value, group=interaction(scenario, type),
                 color = scenario, linetype = type))+
    theme2use +
    theme(axis.text.x = element_text(angle = 90, size=7, vjust=0.5, hjust=1),
          axis.text.y = element_text(size=7),
          axis.title.y = element_text(size=7),
          title = element_text(size=7),
          legend.text = element_text(size=7),
          strip.text = element_text(size=7))+
    labs(y = "[million Veh]", x="")+
      scale_color_manual("Scenario", values = cols)+
      scale_linetype_manual("Lifestyle", values = c(1,2))
    return(plot = list(plot_all = plot_all, plot_reg = plot_reg))
}

p=vintcomparisontotpf(dt = fleet_all, rp = regionplot)
p
aspect_ratio <- 1.5
height <- 3
ggsave("numvehicles.png", p$plot_reg, dpi=500, height = height , width = height * aspect_ratio)

```


## Sales composition

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
salescompf = function(dt){

  plot = ggplot()+
    geom_bar(data = dt, aes(x=as.numeric(as.character(year)),y=shareFS1, group = technology, fill = technology), position = position_stack(), stat = "identity")+
    facet_grid(region ~ scenario)+
    theme2use +
    scale_fill_manual("Technology", values = cols)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2015, 2030, 2050, 2100))+
    labs(x = "", y = "[%]", title = "Market share of new LDV sales")
  return(plot)
}

salescompf(salescomp_all)

```

## Final energy, road

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
EJroadpf = function(dt){
  dt[, technology := factor(technology, levels = legend_ord)]
  dt = dt[year >= 2020]
  plotLDV = ggplot()+
    geom_area(data = dt[subsector_L1 == "trn_pass_road_LDV_4W"], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "LDV Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotBus = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_pass_road_bus_tmp_subsector_L1", "Bus_tmp_subsector_L1")], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Buses Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotTruck = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_freight_road_tmp_subsector_L1")], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Trucks Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  return(plotlist = list(plotLDV = plotLDV, plotBus = plotBus, plotTruck = plotTruck))
}

EJroadpf(EJroad_all)

```

## Final energy, by mode

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
EJmodepf = function(dt){
  dt = dt[year >= 2020]
  plot = ggplot()+
    geom_area(data = dt, aes(x=year, y=demand_EJ, group = interaction(vehicle_type_plot,aggr_mode), fill = vehicle_type_plot), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Total transport final energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use

  return(plot)
}

EJmodepf(EJmode_all)

```

## Energy services, per capita, by mode

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
ESmodecappf = function(dt, rp){
  dt[, vehicle_type_plot := factor(vehicle_type_plot, levels = legend_ord)]
  plot_frgt = ggplot()+
    geom_area(data = dt[mode == "freight" & year >= 2020], aes(x=year, y=cap_dem, group = vehicle_type_plot, fill = vehicle_type_plot), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "Energy Services demand [tkm/cap]")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use


  plot_pass = ggplot()+
    geom_area(data = dt[mode == "pass" & year >= 2020], aes(x=year, y=cap_dem, group = vehicle_type_plot, fill = vehicle_type_plot), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "Energy Services demand [pkm/cap]")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use

      dt[, type := ifelse(grepl("Wise",scenario), "WiseWays", "UsualUse"), by = c("region", "year", "scenario")]
    dt[, scenario := ifelse(grepl("NDC", scenario), "NDC", scenario)]
    dt[, scenario := gsub(".*_", "", scenario)]
    dt[, scenario := gsub("Wise", "", scenario)]

  plot_pass_regi = ggplot()+
    geom_area(data = dt[mode == "pass" & year >= 2020 & year <= 2050 & region == rp & scenario == "NDC"], aes(x=year, y=cap_dem, group = vehicle_type_plot, fill = vehicle_type_plot), alpha = 0.9, color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "Energy Services demand [pkm/cap]")+
    facet_grid(~type)+
    scale_fill_manual("Transport mode",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use


    return(list(plot_pass = plot_pass, plot_frgt = plot_frgt, plot_pass_regi = plot_pass_regi))
}


p = ESmodecappf(ESmodecap_all, rp = regionplot)

p$plot_frgt

p$plot_pass

if (any(grepl("NDC_ConvCase$", unique(ESmodecap_all$scenario))) & any(grepl("NDC_ConvCaseWise", unique(ESmodecap_all$scenario)))){
  print(paste0("Focus on ", regionplot, " in NDC"))

  p$plot_pass_regi

  aspect_ratio <- 1.5
  height <- 6
  ggsave("demmod_wisenormal.png", p$plot_pass_regi, dpi=500, height = height , width = height * aspect_ratio)
}

```

## CO2 intensity of new sales

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}

CO2km_int_newsalespf = function(dt){
  dt = dt[!is.na(gCO2_km_ave)]
  plot = ggplot()+
    geom_line(data = dt[year >= 2020], aes(x = year, y = gCO2_km_ave, group = scenario, color = scenario))+
    labs(title = expression(paste(CO["2"], " intensity of LDVs new additions")), y = expression(paste("[", gCO["2"], "/km]")), x = "")+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030, 2050, 2100))+
    facet_grid(~region)+
    guides(linetype = FALSE) +
    theme2use
  return(plot)
}

CO2km_int_newsalespf(CO2km_int_newsales_all)
```

## Final energy, by fuel

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## passenger by fuel
EJfuels_pf = function(dt_p, dt_f){
  dt_p = dt_p[year >= 2020]
  dt_p = dt_p[, .(demand_EJ = sum(demand_EJ)), by = c("subtech", "year", "region", "scenario")]
  plotp = ggplot()+
    geom_area(data = dt_p, aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Passenger transport FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

    dt_f = dt_f[year >= 2020]

  plotf_lo = ggplot()+
    geom_area(data = dt_f[sector == "trn_shipping_intl"], aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "International freight FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  plotf_sm = ggplot()+
    geom_area(data = dt_f[sector == "trn_freight"], aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Short-medium freight FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  plot = list(plotf_lo = plotf_lo, plotf_sm = plotf_sm, plotp = plotp)
  return(plot)
}

EJfuels_pf(dt_p = EJpass_all, dt_f = EJfrgt_all)
```

## Emissions from demand

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
emidem_pf = function(dt){
 dt[, scenario := as.character(scenario)]
 dt = dt[,.(value = sum(value)), by = c("region","year","scenario")]
  plot = ggplot()+
    geom_line(data = dt, aes(x = year, y = value, group = scenario, color = scenario))+
    labs(x = "", y = "CO2 emissions [Mt/CO2]", title = "Emissions from transport demand (including biofuels)")+
    facet_grid(~region) +
    theme2use

  return(plot)
}

emidem_pf(emidem_all)
```

## Electricity demand

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
elecdem_pf = function(dt, rp){
 dt[, scenario := as.character(scenario)]
 dt[, type := ifelse(grepl("Wise",scenario), "WiseWays", "UsualUse"), by = c("region", "year", "scenario")]
 dt[, scenario := ifelse(grepl("NDC", scenario), "NDC", scenario)]
 dt[, scenario := gsub(".*_", "", scenario)]
 dt[, scenario := gsub("Wise", "", scenario)]

  plot_all = ggplot()+
    geom_line(data = dt, aes(x = year, y = value, group = interaction(scenario, type), color = scenario, linetype = type))+
    labs(x = "", y = "Secondary electricity [EJ]")+
    facet_grid(~region) +
    theme2use +
     scale_linetype_manual("", values = c(1,2))+
     scale_color_manual("Scenario", values = cols)

   plot_regi = ggplot()+
    geom_line(data = dt[region == rp & year <= 2050], aes(x = year, y = value, group = interaction(scenario, type), color = scenario, linetype = type))+
    labs(x = "", y = "Secondary electricity [EJ]") +
    theme2use +
     scale_linetype_manual("Lifestyle", values = c(1,2))+
     scale_color_manual("Scenario", values = cols)

  plot = list(plot_all = plot_all, plot_regi = plot_regi)
  return(plot)
}

p = elecdem_pf(elecdem_all, rp = regionplot)

p$plot_all

print(paste0("Focus on ", regionplot))

p$plot_regi

aspect_ratio <- 1.5
height <- 6
ggsave("elecdemand.png", p$plot_regi, dpi=500, height = height , width = height * aspect_ratio)



```



## Demand per capita VS gdp per capita
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
demcapgdpcap_pf = function(dt) {

dt = dt[year >= 2005]
dt = dt[, year := as.character(year)]
dtsec = unique(dt[, c("region", "year", "demsec", "sector", "gdpcap", "scenario")])
psec = ggplot()+
 geom_line(data = dtsec, aes(x = gdpcap, y = demsec, color = region, group = interaction(region, scenario), linetype = scenario))+
 geom_point(data = dtsec[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = gdpcap, y = demsec, shape = year, group = interaction("region", "scenario"), color = region))+
  facet_wrap(~sector, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")



dtappl = unique(dt[, c("region", "year", "demappl", "appl", "gdpcap", "scenario")])
pappl = ggplot()+
  geom_line(data = dtappl, aes(x = gdpcap, y = demappl, color = region, group = interaction(region, scenario), linetype = scenario))+
  geom_point(data = dtappl[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = gdpcap, y = demappl, shape = year, group = region, color = region))+
  facet_wrap(~appl, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")


dttype = unique(dt[, c("region", "year", "demtype", "type", "gdpcap", "scenario")])
ptype = ggplot()+
  geom_line(data = dttype, aes(x = gdpcap, y = demtype, color = region, group = interaction(region, scenario), linetype = scenario))+
  geom_point(data = dttype[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = gdpcap, y = demtype, shape = year, group = region, color = region))+
  facet_wrap(~type, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")

psectime = ggplot()+
  geom_line(data = dtsec, aes(x = year, y = demsec, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~sector, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")


pappltime = ggplot()+
  geom_line(data = dtappl, aes(x = year, y = demappl, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~appl, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")


ptypetime = ggplot()+
  geom_line(data = dttype, aes(x = year, y = demtype, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~type, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")



p = list(psec = psec, pappl = pappl, ptype = ptype, psectime = psectime, pappltime = pappltime, ptypetime = ptypetime)

return(p)
}

demcapgdpcap_pf(dempkm_cap_all)
```

## Focus on selected region

## Vintages
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}

## only in case there are 10 scenarios (5 scenarios for each lifestyle realization) the following chunk of code is to be run
if (length(unique(fleet_all$scenario)) == 10 & any(grepl("Wise", unique(fleet_all$scenario)))) {

vintcomparison_regi_pf = function(dt, rp){
  dt = dt[year %in% c(2020, 2030, 2050) & region == rp]

  ## define the maximum on the y-axis depending on the maximum value across scenarios
  dt[, sum := sum(value), by = c("year", "scenario")]
  dt[, maxval := max(sum)]
  dthist = dt[year == 2020 & scenario == unique(dt$scenario)[1]][, scenario := "Historical"]
  ## attribute "type" WiseWays and UsualUse and simplify scenario names
  dt[, type := ifelse(grepl("Wise",scenario), "WiseWays", "UsualUse"), by = c("region", "year", "scenario")]
  dt[, scenario := ifelse(grepl("NDC", scenario), "NDC", scenario)]
  dt[, scenario := gsub(".*_", "", scenario)]
  dt[, scenario := gsub("Wise", "", scenario)]

  ## select a random scenario for 2020 and attribute the label "Historical" (no value on the x axis)
  phist_no_name = ggplot()+
    geom_bar(data = dthist,
             aes(x=scenario, y=value, group= technology,
                 fill = technology, width=.75), position="stack", stat = "identity", width = 0.5, alpha = 0.9)+
    ylim(0,unique(dt[, maxval]))+
    facet_wrap(~ year, nrow = 1)+
    theme2use +
    theme(axis.text.x = element_blank(),
          legend.position = "none")+
    scale_fill_manual(values = cols)+
    labs(y = "[million Veh]", x="")

  ## historical plot, with name on the x axis
  phist = phist_no_name+
    theme(axis.text.x = element_text(angle = 90, size=14, vjust=0.5, hjust=1))


  ## Usual Use scenarios (no names on the x-axis, as it's going to be the top row)
  pnormal = ggplot()+
    geom_bar(data = dt[year != 2020 & !grepl("Wise", type)],
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, width=.75), position="stack", stat = "identity", width = 0.5, alpha = 0.9)+
    theme2use +
    ylim(0,unique(dt[, maxval]))+
    facet_grid(type ~ year)+
    theme(axis.text.x = element_blank(),
          axis.text.y = element_blank())+
    guides(fill=guide_legend(title="Powertrain"))+
    scale_fill_manual(values = cols)+
    labs(y = "", x="")

    ## WiseWays scenarios (names on the x-axis)
    pwise = ggplot()+
    geom_bar(data = dt[year != 2020 & grepl("Wise", type)],
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, width=.75), position="stack", stat = "identity", width = 0.5, alpha = 0.9)+
    ylim(0,unique(dt[, maxval]))+
    facet_grid(type ~ year)+
    theme2use +
    guides(fill=guide_legend(title="Powertrain"))+
    scale_fill_manual(values = cols)+
    labs(y = "", x="")

   ## get legend of plots
   techlegend <- get_legend(pwise)

   ## remove legend from plots
   pwise = pwise +
   theme(legend.position = "none")

   pnormal = pnormal +
   theme(legend.position = "none")

   ## first row
   plot1 = plot_grid(phist_no_name, pnormal, align = "h", ncol = 2, rel_widths = c(0.16,0.84))
   ## second row
   plot2 = plot_grid(phist, pwise, align = "h", ncol = 2, rel_widths = c(0.16,0.84))
   ## both bar plots
   plot3 = plot_grid(plot1, plot2, align = "v", ncol = 1, rel_heights = c(0.45,0.55))
   ## create legend stacked with blank sqares to have it centered
   blank <- grid.rect(gp=gpar(col="white"))
   techlegend = plot_grid(blank, techlegend, blank, align = "h", ncol = 1, rel_heights  = c(0.05, 0.7,0.25))
   ## combine all elements in final plot
   plotvint = plot_grid(plot3, techlegend, align = "h", ncol = 2, rel_widths  = c(0.8,0.2))

   return(plotvint)
}

p = vintcomparison_regi_pf(fleet_all, rp = regionplot)

p


aspect_ratio <- 1.5
height <- 8
ggsave("pvint.png", p, dpi=500, height = height , width = height * aspect_ratio)

}
```

## Costs of LDVs by technology

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
costspf = function(dt, rp, mapping_scens){
  dt = dt[region == rp]
  map = data.table(name = c("Risk", "Charging", "Model availability", "Range anxiety", "Refuel availability", "Fuel", "Policy induced inconvenience", "Purchase", "O&M"),
                   logit_type = c("prisk", "pchar", "pmod_av", "prange", "pref", "fuel_price", "pinco_tot", "purchase", "other"),
                   type = c("inc", "inc", "inc", "inc", "inc", "real", "inc", "real", "real"))
  dt = merge(dt, map, by = "logit_type")
  dt_inc = dt[type == "inc"]
  dt_inc = dt_inc[,.(cost = sum(cost)), by = c("region", "year", "type", "technology", "scenario")]
  dt_tot = rbind(dt_inc[, c("name", "logit_type") := list("Inconvenience", "pinc")], dt[type == "real"])
  dt[, name := factor(name, levels = legend_ord)]
  dt_tot[, name := factor(name, levels = legend_ord)]
  dt_tot[, alph := ifelse(logit_type=="pinc", 0.6, 0.9)]

  dt = merge(dt, mapping_scens, by = "scenario")
  dt[, scen_name := ifelse(is.na(scen_name), scenario, scen_name)]

  dt_tot = merge(dt_tot, mapping_scens, by = "scenario")
  dt_tot[, scen_name := ifelse(is.na(scen_name), scenario, scen_name)]

  plot1 = ggplot()+
         geom_bar(data = dt[type == "inc"], aes(x = year, y = cost, group = name, fill = name), position = "stack", stat = "identity")+
facet_grid(scen_name~technology) +
    theme2use +
    guides(fill=guide_legend(title="Cost component"))+
    scale_fill_manual(values = cols)+
    labs(y = "Costs [$/pkm]", x="")

  plot2 = ggplot()+
         geom_bar(data = dt_tot, aes(x = year, y = cost, group = name, fill = name, alpha = alph), position = "stack", stat = "identity")+
facet_grid(scen_name~technology)+
    theme2use +
    scale_fill_manual(values = cols)+
    labs(y = "Costs [$/pkm]", x="")+
      scale_alpha(range=c(0.4,1)) +
  guides(alpha=FALSE, linetype=FALSE,
         fill=guide_legend(reverse=TRUE, title="Cost component"))

  if (length(unique(dt$scenario)) == 10) {
    ## plot only UsualUse
    plot3 = ggplot()+
         geom_bar(data = dt[type == "inc" & year %in% c(2020, 2050)& !grepl(pattern = "Wise", scen_name)], aes(x = as.character(year), y = cost, group = name, fill = name), alpha = 0.9, position = "stack", stat = "identity")+
facet_grid(scen_name~technology)+
    theme2use +
    guides(fill=guide_legend(title="Cost component"))+
    scale_fill_manual(values = cols)+
    labs(y = "Costs [$/pkm]", x="")

  plot4 = ggplot()+
         geom_bar(data = dt_tot[year %in% c(2020, 2050) & !grepl(pattern = "Wise",scen_name)], aes(x = as.character(year), y = cost, group = name, fill = name, alpha = alph), position = "stack", stat = "identity")+
facet_grid(scen_name~technology)+
    theme2use +
    scale_fill_manual(values = cols)+
    labs(y = "Costs [$/pkm]", x="")+
      scale_alpha(range=c(0.4,1)) +
  guides(alpha=FALSE, linetype=FALSE,
         fill=guide_legend(reverse=TRUE, title="Cost component"))


  plot = list(plot1 = plot1, plot2 = plot2, plot3 = plot3, plot4 = plot4)

  }
  else{
    plot = list(plot1 = plot1, plot2 = plot2)
  }


return(plot)
}

p = costspf(costs_all, rp = regionplot, mapping_scens)

p$plot1
p$plot2

if (!is.null(p$plot3)) {

  print(paste0("Focus on ", regionplot, " for Usual Use"))
  p$plot3
  p$plot4

  aspect_ratio <- 2
  height <- 6

  ggsave("LDVinccost.png", p$plot3, dpi=500, height = height , width = height * aspect_ratio)
  ggsave("LDVtotcost.png", p$plot4, dpi=500, height = height , width = height * aspect_ratio)

}



```

## Sales composition

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
salescom_regi_pf = function(dt, rp){

  plot = ggplot()+
    geom_area(data = dt[region == rp], aes(x=as.numeric(as.character(year)), y = shareFS1, group = technology, fill = technology), position = position_fill())+
    facet_wrap( ~ scenario, nrow = 1)+
    scale_fill_manual("Technology", values = cols)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2015,2030,2050, 2100))+
    scale_y_continuous(labels = scales::percent)+
    theme2use +
    labs(x = "", y = "[%]", title = "Market share of new LDV sales")
  return(plot)
}

p = salescom_regi_pf(salescomp_all, rp = regionplot)

p

aspect_ratio <- 2
height <- 5
ggsave("psales.png", p, dpi=500, height = height , width = height * aspect_ratio)


```


## CO2 intensity of new sales

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
CO2km_int_regi_newsalespf = function(dt, rp){
  dt = dt[!is.na(gCO2_km_ave)]
  if (rp == "EUR"){
    ## add historical values
  historical_values = data.table(year = c(2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018), emi = c(159, 157, 145, 140, 137, 132, 128, 124, 120, 119, 119, 120))

  targets = data.table(name = c("2021 target", "2025 target", "2030 target"), value = c(95, 95*(1-0.15), 95*(1-0.37)))

  dt[, type := ifelse(grepl("Wise",scenario), "WiseWays", "UsualUse"), by = c("region", "year", "scenario")]
    dt[, scenario := ifelse(grepl("NDC", scenario), "NDC", scenario)]
    dt[, scenario := gsub(".*_", "", scenario)]
    dt[, scenario := gsub("Wise", "", scenario)]

   plot = ggplot()+
    geom_line(data = dt[year >= 2020 & year <= 2050 & region == rp], aes(x = year, y = gCO2_km_ave, group = interaction(scenario, type), color = scenario, linetype = type))+
    geom_point(data = historical_values, aes(x = year, y = emi), color = "grey20")+
    geom_point(data = targets, aes(x = c(2021, 2025, 2030), y = value, shape = name), color = "grey20", alpha = 0.5, size = 2)+
    geom_text(data = targets, aes(y = value+5, x = c(2021, 2025, 2030), label = name), size = 5)+
    labs(y = expression(paste("[", gCO["2"], "/km]")), x = "")+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2010, 2020, 2030, 2050, 2100))+
    theme2use +
    guides(shape = FALSE)+
    scale_linetype_manual("Lifestyle", values = c(1,2))

  } else {
  ## historical values are not available
  plot = ggplot()+
    geom_line(data = dt[year >= 2020 & region == rp], aes(x = year, y = gCO2_km_ave, group = scenario, color = scenario))+
    labs(y = expression(paste("[", gCO["2"], "/km]")), x = "")+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030, 2050, 2100))+
    theme2use +
    guides(linetype = FALSE)

   }
  return(plot)
}

p = CO2km_int_regi_newsalespf(CO2km_int_newsales_all, rp = regionplot)

p

```

## Final energy road

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
EJroad_regi_pf = function(dt, rp){
  dt[, technology := factor(technology, levels = legend_ord)]
  dt = dt[year >= 2020]
  plotLDV = ggplot()+
    geom_area(data = dt[subsector_L1 == "trn_pass_road_LDV_4W" & region == rp], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "LDV Final Energy demand")+
    facet_wrap(~scenario, nrow = 1)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotBus = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_pass_road_bus_tmp_subsector_L1", "Bus_tmp_subsector_L1") & region == rp], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Buses Final Energy demand")+
    facet_wrap(~scenario, nrow = 1)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotTruck = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_freight_road_tmp_subsector_L1") & region == rp], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Trucks Final Energy demand")+
    facet_wrap(~scenario, nrow = 1)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  return(plotlist = list(plotLDV = plotLDV, plotBus = plotBus, plotTruck = plotTruck))
}

plist = EJroad_regi_pf(EJroad_all, rp = regionplot)

plist

pLDV = plist[["plotLDV"]]

pBus = plist[["plotBus"]]

pTruck = plist[["plotTruck"]]

```
