# |  (C) 2006-2020 Potsdam Institute for Climate Impact Research (PIK)
# |  authors, and contributors see CITATION.cff file. This file is part
# |  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
# |  AGPL-3.0, you are granted additional permissions described in the
# |  REMIND License Exception, version 1.0 (see LICENSE file).
# |  Contact: remind@pik-potsdam.de

---
title: "Compare scenarios Transport"
output:
  pdf_document: default
  html_document:
    df_print: paged
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = 'pdf')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
require(ggplot2)
require(mrremind)
require(rmndt)
require(quitte)
library(lucode2)
library(magpie)
library(quitte)
library(cowplot)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Set RDS files path
EJmode_all = readRDS("EJmode_all.RDS")
EJroad_all = readRDS("EJroad_all.RDS")
fleet_all = readRDS("fleet_all.RDS")
salescomp_all = readRDS("salescomp_all.RDS")
ESmodecap_all = readRDS("ESmodecap_all.RDS")
EJpass_all = readRDS("EJfuelsPass_all.RDS")
EJfrgt_all = readRDS("EJfuelsFrgt_all.RDS")
EJModeFuel_all = readRDS("EJModeFuel_all.RDS")
emidem_all = readRDS("emidem_all.RDS")
costs_all = readRDS("costs_all.RDS")
pref_FV_all = readRDS("pref_FV_all.RDS")
dempkm_cap_all = readRDS("demgdpcap_all.RDS")
setConfig(forcecache=T)

cols <- c("NG" = "#d11141",
          "Gases" = "#d11141",
          "Coal" = "#113245",
          "Hydro" = "#87cefa",
          "Solar" = "#edae49",
          "Geothermal" = "#58b4ae",
          "Uranium" = "orchid",
          "Wind" = "#e43f5a",
          "Liquids" = "#8c8c8c",
          "Hybrid Liquids" = "#ffc425",
          "Hybrid Electric" = "#f37735",
          "BEV" = "#00b159",
          "Electricity" = "#00b159",
          "Electric" = "#00b159",
          "FCEV" = "#00aedb",
          "Hydrogen" = "#00aedb",
          "Biodiesel" = "#66a182",
          "Biomass" = "#66a182",
          "Synfuel" = "orchid",
          "Synfuels" = "orchid",
          "Oil" = "#2e4057",
          "O&M" = "#edae49",
          "Range anxiety" = "#e43f5a",
          "Refuel availability" = "#f79071",
          "Purchase" = "#d1495b",
          "Model availability" = "#58b4ae",
          "Inconvenience" = "#58b4ae",
          "Charging" = "#007892",
          "Policy induced inconvenience" = "#2e4057",
          "Risk" = "#feb72b",
          "Fuel" = "#035aa6",
          "International Aviation" = "#9acd32",
          "Domestic Aviation" = "#7cfc00",
          "Bus" = "#32cd32",
          "Passenger Rail" = "#2e8b57",
          "Freight Rail" = "#ee4000",
          "Trucks" = "#ff6a6a",
          "International Shipping" = "#cd2626",
          "Domestic Shipping" = "#ff4040",
          "Shipping" = "#ff4040",
          "Truck" = "#ff7f50",
          "Trucks (<3.5t)" = "#ff7f50",
          "Trucks (3.5t-16)" = "#8b0000",
          "Trucks (>16)" = "#fa8072",
          "Motorbikes" = "#1874cd",
          "Small Cars" = "#87cefa",
          "Large Cars" = "#6495ed",
          "Van" = " 	#40e0d0",
          "LDV" = "#00bfff",
          "Non motorized" = "#da70d6",
          "Freight"="#ff0000",
          "Freight (Inland)" = "#cd5555",
          "Pass non LDV" = "#6b8e23",
          "Pass" = "#66cdaa",
          "Pass non LDV (Domestic)" = "#54ff9f",
          "refined liquids enduse" = "#8c8c8c",
          "FE|Transport|Hydrogen" = "#00aedb",
          "FE|Transport|NG" = "#d11141",
          "FE|Transport|Liquids" = "#8c8c8c",
          "FE|Transport|Electricity" = "#00b159",
          "FE|Transport" = "#1e90ff",
          "FE|Buildings" = "#d2b48c",
          "FE|Industry" = "#919191",
          "LDVs Electricity" = "#00b159",
          "Bus+Rail Electricity" = "#7cfc00",
          "Road+Rail freight Electricity" = "#68c6a4",
          "LDVs Hydrogen" = "#00aedb",
          "Bus+Rail Hydrogen" = "#00bfff",
          "Road+Rail freight Hydrogen" = "#035aa6",
          "Domestic Aviation Hydrogen" = "#a5d7f1",
          "LDVs Hydrocarbons" = "#8c8c8c",
          "Bus+Rail Hydrocarbons" = "#b2b2b2",
          "Road+Rail freight Hydrocarbons" = "#787f77",
          "Domestic Aviation Hydrocarbons" = "#d7d7d7",
          "Domestic Shipping Hydrocarbons" = "#978888",
          "International Aviation Hydrocarbons" = "#474847",
          "International Shipping Hydrocarbons" = "#53515b")

legend_ord_modes <- c("Freight Rail", "Truck", "Shipping", "International Shipping", "Domestic Shipping",  "Trucks",
                "Motorbikes", "Small Cars", "Large Cars", "Van",
                "International Aviation", "Domestic Aviation","Bus", "Passenger Rail",
                "Freight", "LDV", "Pass non LDV", "Freight (Inland)", "Pass non LDV (Domestic)", "Non motorized")
legend_ord_modes_fuel <- c("LDVs Electricity", "Bus+Rail Electricity", "Road+Rail freight Electricity",
                           "LDVs Hydrogen", "Bus+Rail Hydrogen", "Road+Rail freight Hydrogen", "Domestic Aviation Hydrogen",
                           "LDVs Hydrocarbons", "Bus+Rail Hydrocarbons", "Road+Rail freight Hydrocarbons", "Domestic Aviation Hydrocarbons", "Domestic Shipping Hydrocarbons", "International Aviation Hydrocarbons", "International Shipping Hydrocarbons")

legend_ord_fuels <- c("BEV", "Electricity", "Electric", "Hybrid Electric", "FCEV", "Hydrogen", "Hybrid Liquids", "Liquids", "Oil", "Biodiesel", "Biofuel", "Biomass", "Synfuel", "Synfuels", "Gases","NG")

legend_ord_costs <- c("Inconvenience", "Risk", "Charging", "Model availability", "Range anxiety", "Refuel availability", "Policy induced inconvenience","Fuel", "Purchase", "O&M")

legend_ord_emissions <- c("Emi|CO2|Industry|Gross", "Emi|CO2|Buildings|Direct", "Emi|CO2|Transport|Demand", "Emi|CO2|Energy|Supply|Gross", "Emi|CO2|Land-Use Change","Emi|CO2|CDR|BECCS")

legend_ord = c(legend_ord_modes, legend_ord_fuels, legend_ord_costs, legend_ord_modes_fuel)

regionplot = "EUR"

## set the theme for the plots
theme2use <- theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, size=14, vjust=0.5, hjust=1),
          axis.text.y = element_text(size=14),
          axis.title.y = element_text(size=14),
          title = element_text(size=14),
          axis.line = element_line(size = 0.5, colour = "grey"),
          legend.text = element_text(size=14),
          strip.text = element_text(size=14),
          strip.background = element_rect(color = "grey"))
```


## Vintages by powertrain

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## Vintages
vintcomparisonpf = function(dt){
  dt = dt[year %in% c(2015, 2050, 2100)]
  plot = ggplot()+
    geom_bar(data = dt,
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, width=.75), alpha = 0.5, position="stack", stat = "identity", width = 0.5)+
    geom_bar(data = dt,
             aes(x=scenario, y=value, group=interaction(variable, technology),
                 fill = technology, alpha = factor(alphaval),  width=.75), position="stack", stat = "identity", width = 0.5, color = "black", size=0.05)+
    guides(fill = guide_legend(reverse=TRUE))+
    facet_grid(year~region, scales = "free") +
    theme2use +
    scale_alpha_discrete(breaks = c(1,0), name = "Status", labels = c("Vintages","New additions")) +
    guides(linetype=FALSE,
           fill=guide_legend(reverse=FALSE, title="Transport mode"))+
    scale_fill_manual(values = cols)+
    labs(y = "[million Veh]", x="", title = "LDV fleet")
    return(plot)
}

vintcomparisonpf(fleet_all)
```

## Sales composition

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}

salescompf = function(dt){
  plot = ggplot()+
    geom_bar(data = dt, aes(x=as.numeric(as.character(year)),y=shareFS1, group = technology, fill = technology), position = position_stack(), stat = "identity")+
    facet_grid(region ~ scenario)+
    theme2use +
    scale_fill_manual("Technology", values = cols)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2015, 2030, 2050, 2100))+
    labs(x = "", y = "[%]", title = "Market share of new LDV sales")
  return(plot)
}

salescompf(salescomp_all)

```

## Final energy, road

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
EJroadpf = function(dt){
  dt[, technology := factor(technology, levels = legend_ord)]
  dt = dt[year >= 2020]
  plotLDV = ggplot()+
    geom_area(data = dt[subsector_L1 == "trn_pass_road_LDV_4W"], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "LDV Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotBus = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_pass_road_bus_tmp_subsector_L1", "Bus_tmp_subsector_L1")], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Buses Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


   plotTruck = ggplot()+
    geom_area(data = dt[subsector_L1 %in% c("trn_freight_road_tmp_subsector_L1")], aes(x=year, y=demand_EJ, group = technology, fill = technology), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Trucks Final Energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology", values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  return(plotlist = list(plotLDV = plotLDV, plotBus = plotBus, plotTruck = plotTruck))
}

EJroadpf(EJroad_all)

```

## Final energy, by mode

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
EJmodepf = function(dt){
  dt = dt[year >= 2020]
  plot = ggplot()+
    geom_area(data = dt, aes(x=year, y=demand_EJ, group = interaction(vehicle_type_plot,aggr_mode), fill = vehicle_type_plot), color = "black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Total transport final energy demand")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use

  return(plot)
}

EJmodepf(EJmode_all)

```

## Energy services, per capita, by mode

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
ESmodecappf = function(dt){
  dt[, vehicle_type_plot := factor(vehicle_type_plot, levels = legend_ord)]
  plot_frgt = ggplot()+
    geom_area(data = dt[mode == "freight" & year >= 2020], aes(x=year, y=cap_dem, group = vehicle_type_plot, fill = vehicle_type_plot), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "Energy Services demand [tkm/cap]")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use


  plot_pass = ggplot()+
    geom_area(data = dt[mode == "pass" & year >= 2020], aes(x=year, y=cap_dem, group = vehicle_type_plot, fill = vehicle_type_plot), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "Energy Services demand [pkm/cap]")+
    facet_grid(scenario~region)+
    scale_fill_manual("Vehicle Type",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020,2030,2050, 2100)) +
    theme2use
    return(list(plot_pass = plot_pass, plot_frgt = plot_frgt))
}

p = ESmodecappf(ESmodecap_all)
```

## Final energy, by fuel
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## all modes by fuel and mode
EJfuelsMod_pf = function(dt_all){
  dt_all = dt_all[year>=2020]
  dt_all[veh %in% c("Small Cars", "Large Cars", "Motorbikes"), veh := "LDVs"]
  dt_all[veh %in% c("Bus", "Passenger Rail"), veh := "Bus+Rail"]
  dt_all[veh %in% c("Truck", "Freight Rail"), veh := "Road+Rail freight"]
  dt_all[technology %in% c("NG", "Liquids"), technology := "Hydrocarbons"]
  dt_all[technology %in% c("BEV", "Electric"), technology := "Electricity"]
  dt_all[technology %in% c("FCEV"), technology := "Hydrogen"]
  dt_all = dt_all[, techmode := paste0(veh, " ", technology)]
  dt_all[, techmode := factor(techmode, levels = legend_ord)]
  dt_all_b = dt_all[, .(demand_EJ = sum(demand_EJ)), by = c("techmode", "year", "region", "scenario")]
  dt_all_nob = dt_all[! veh %in% c("International Aviation", "International Shipping")][, .(demand_EJ = sum(demand_EJ)), by = c("techmode", "year", "region", "scenario")]

  plot_b_lo = ggplot()+
    geom_area(data = dt_all_b, aes(x=year, y=demand_EJ, group = techmode, fill = techmode), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "All transport demand by fuel")+
    facet_grid(scenario~region, scales = "free")+
    scale_fill_manual("Transport mode",values = cols, breaks = legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  plot_nb_lo = ggplot()+
    geom_area(data = dt_all_nob, aes(x=year, y=demand_EJ, group = techmode, fill = techmode), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "All transport demand by fuel, no bunkers")+
    facet_grid(scenario~region, scales = "free")+
    scale_fill_manual("Transport mode",values = cols, breaks = legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  plot = list(plot_b_lo = plot_b_lo, plot_nb_lo = plot_nb_lo)
  return(plot)
}

EJfuelsMod_pf(dt_all = EJModeFuel_all)
```



```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
## by  fuel, transport aggregated
EJfuels_pf = function(dt_p, dt_f){
  dt_p = dt_p[year >= 2020]
  dt_p = dt_p[, .(demand_EJ = sum(demand_EJ)), by = c("subtech", "year", "region", "scenario", "sector")]
  plotp = ggplot()+
    geom_area(data = dt_p, aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Passenger transport FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

    dt_f = dt_f[year >= 2020]
    dt_f = dt_f[, .(demand_EJ = sum(demand_EJ)), by = c("subtech", "year", "region", "scenario", "sector")]
  plotf_lo = ggplot()+
    geom_area(data = dt_f[sector == "trn_shipping_intl"], aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "International freight FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use

  plotf_sm = ggplot()+
    geom_area(data = dt_f[sector == "trn_freight"], aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "Short-medium freight FE demand by fuel")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use
  dt_all = rbind(dt_f, dt_p)
  dt_all_b = dt_all[, .(demand_EJ = sum(demand_EJ)), by = c("subtech", "year", "region", "scenario")]
  plot_all = ggplot()+
    geom_area(data = dt_all_b, aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "FE demand by fuel, all transport modes")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use
  dt_all_nob = dt_all[sector %in% c("trn_pass", "trn_freight")][, .(demand_EJ = sum(demand_EJ)), by = c("subtech", "year", "region", "scenario")]

  plot_all_nobunkers = ggplot()+
    geom_area(data = dt_all_nob, aes(x=year, y=demand_EJ, group = subtech, fill = subtech), color="black", size=0.05, position= position_stack())+
    labs(x = "", y = "[EJ]", title = "FE demand by fuel, all transport modes")+
    facet_grid(scenario~region)+
    scale_fill_manual("Technology",values = cols, breaks=legend_ord)+
    expand_limits(y = c(0,1))+
    scale_x_continuous(breaks = c(2020, 2030,2050, 2100)) +
    theme2use


  plot = list(plotf_lo = plotf_lo, plotf_sm = plotf_sm, plotp = plotp, plot_all = plot_all, plot_all_nobunkers = plot_all_nobunkers)
  return(plot)
}

EJfuels_pf(dt_p = EJpass_all, dt_f = EJfrgt_all)
```

## Emissions from demand

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
emidem_pf = function(dt){
 dt[, scenario := as.character(scenario)]
 dt = dt[,.(value = sum(value)), by = c("region","year","scenario")]
  plot = ggplot()+
    geom_line(data = dt, aes(x = year, y = value, group = scenario, color = scenario))+
    labs(x = "", y = "CO2 emissions [Mt/CO2]", title = "Emissions from transport demand (including biofuels)")+
    facet_grid(~region) +
    theme2use
  return(plot)
}
emidem_pf(emidem_all)
```


## Demand per capita VS gdp per capita
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}
demcapgdpcap_pf = function(dt) {
dt = dt[year >= 2005]
dt = dt[, year := as.character(year)]
dtsec = unique(dt[, c("region", "year", "demsec", "sector", "GDP_cap", "scenario")])
psec = ggplot()+
 geom_line(data = dtsec, aes(x = GDP_cap, y = demsec, color = region, group = interaction(region, scenario), linetype = scenario))+
 geom_point(data = dtsec[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = GDP_cap, y = demsec, shape = year, group = interaction("region", "scenario"), color = region))+
  facet_wrap(~sector, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")



dtappl = unique(dt[, c("region", "year", "demappl", "appl", "GDP_cap", "scenario")])
pappl = ggplot()+
  geom_line(data = dtappl, aes(x = GDP_cap, y = demappl, color = region, group = interaction(region, scenario), linetype = scenario))+
  geom_point(data = dtappl[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = GDP_cap, y = demappl, shape = year, group = region, color = region))+
  facet_wrap(~appl, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")


dttype = unique(dt[, c("region", "year", "demtype", "type", "GDP_cap", "scenario")])
ptype = ggplot()+
  geom_line(data = dttype, aes(x = GDP_cap, y = demtype, color = region, group = interaction(region, scenario), linetype = scenario))+
  geom_point(data = dttype[year %in% c("2020", "2030", "2050", "2070", "2100")], aes(x = GDP_cap, y = demtype, shape = year, group = region, color = region))+
  facet_wrap(~type, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="GDP per capita [$/person]")

psectime = ggplot()+
  geom_line(data = dtsec, aes(x = year, y = demsec, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~sector, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")


pappltime = ggplot()+
  geom_line(data = dtappl, aes(x = year, y = demappl, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~appl, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")


ptypetime = ggplot()+
  geom_line(data = dttype, aes(x = year, y = demtype, color = region, group = interaction(region, scenario), linetype = scenario))+
  facet_wrap(~type, scales = "free") +
  theme2use +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        title = element_text(size=8),
        legend.title = element_text(size=10),
        axis.title = element_text(size = 10))+
  labs(y = "Per capita demand [km/capita]", x="")
p = list(psec = psec, pappl = pappl, ptype = ptype, psectime = psectime, pappltime = pappltime, ptypetime = ptypetime)
return(p)
}
demcapgdpcap_pf(dempkm_cap_all)
```

