---
title: "Transport decarbonization dashboard"
author: ""
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
runtime: flexdashboard
---



```{r loading_required_libraries, include=FALSE}
  #Loading required libraries
  library(flexdashboard)
  library(ggplot2)
  library(plotly)
  library(magclass)
  library(mip)
  library(data.table)
```



```{r creating_charts, include=FALSE}
source("helper_dashboard.R")

legend=plotlist$legend

```

```{r global_options, include=FALSE}
  # setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svg', fig.asp = 1 ) # fig.asp = default aspect ratio
```

```{r creating_info_tooltips, include=FALSE}
  #data frame with help tooltips

  helpTooltip_df <- data.frame(
    title=c("Per capita Passenger Transport Energy Services Demand", "Per capita Freight Transport Energy Services Demand", "Sales composition", "Final energy LDVs by fuel","Transport Final Energy Demand", "Fleet composition"),
    placement=c("right", "left", "right", "left", "left", "left"))


helpTooltip = function(tooltipdf){
  
  title <- as.character(tooltipdf$title) 
  placement <- as.character(tooltipdf$placement) 
  
  contents <- gsub('\n', '',gsub('"', '&quot;',paste0('
<div class="tooltipContainer">
  <div class="tooltipDescription">',
    legend[[title]]$description,'
  </div>
  <div class="legendContainer">
  	<table class="legendTable">
  		<tbody>
  			<tr>',
	      do.call(paste,lapply(names(legend[[title]]$contents),function(x){
        paste0('<tr><td>',
          ifelse(is.null(legend[[title]]$contents[[x]]$linetype),
                  paste0('<div class="square"><div class="circle" style="background-color:',legend[[title]]$contents[[x]]$fill,';"></div></div>'),
  				        paste0('<div class="line" style="border-color:',legend[[title]]$contents[[x]]$fill,'; border-style: ',legend[[title]]$contents[[x]]$linetype,';"></div>')
  				        ),'
            </td><td class="legendText">',x,'</td></tr>'
           )
  	    })),'
  		</tbody>
  	</table>
  </div>
</div>')))
  
  result = ""
  result = paste0(result,"<script type='text/javascript'>\n");
  result = paste0(result,"$(window).load(function () {\n");
  result = paste0(result,"  $('.chart-title').filter(function() { return $(this).clone().children().remove().end().text() == '", title, "' }).each(function(){\n");
  if(!(placement == "none"))
    result = paste0(result,"  	$(this).append('<i class=\"glyphicon glyphicon-info-sign infoIcon\" data-toggle=\"tooltip\" data-html=\"true\" data-placement=\"right\" title=\"",contents,"\"></i>');\n");
  result = paste0(result,"  	$(this).find('[data-toggle=\"tooltip\"]').tooltip({ placement:'",placement,"'});\n");
  result = paste0(result,"	})\n");
  result = paste0(result,"})\n");
  result = paste0(result,"</script>");

  return(result)
}

```

<!--############################# -->
<!--#### START OF MENUS CODE #### -->
<!--############################# -->

<!-- ### Creating main emissions menu ### -->

<!--Creating First Page - LDV Page-->
Overview {data-icon="glyphicon glyphicon-scale"}
===================================== 
Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#overview){class="glyphicon glyphicon-oil sidebar-button selected"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case", icon = "glyphicon-oil")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ConvCase$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Conventional patterns.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$ConvCase$plot$ESmodecap_pass
```

### Per capita Freight Transport Energy Services Demand
```{r}
plotlist$ConvCase$plot$ESmodecap_frgt
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Final Energy Demand

```{r}
plotlist$ConvCase$plot$EJfuels
```

### Emissions transport demand

```{r}
plotlist$ConvCase$plot$emidem
```

Overview FCEV scenario {.hidden data-icon="glyphicon glyphicon-tint"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#overview){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button selected"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Hydrogen Hype", icon = "glyphicon-tint")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$HydrHype$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for hydrogen vehicles.

<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$HydrHype$plot$ESmodecap_pass
```

### Per capita Freight Transport Energy Services Demand
```{r}
plotlist$HydrHype$plot$ESmodecap_frgt
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Final Energy Demand

```{r}
plotlist$HydrHype$plot$EJfuels
```

### Emissions transport demand

```{r}
plotlist$HydrHype$plot$emidem
```

Overview BEV scenario { .hidden data-icon="glyphicon glyphicon-flash"}
===================================== 


Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#overview){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button selected"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Electric Era", icon = "glyphicon-flash")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ElecEra$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for battery electric vehicles.


<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$ElecEra$plot$ESmodecap_pass
```

### Per capita Freight Transport Energy Services Demand
```{r}
plotlist$ElecEra$plot$ESmodecap_frgt
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Final Energy Demand

```{r}
plotlist$ElecEra$plot$EJfuels
```

### Emissions transport demand

```{r}
plotlist$ElecEra$plot$emidem
```

Overview Synfuel scenario {.hidden data-icon="glyphicon glyphicon-random"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#overview){class="glyphicon glyphicon-oil sidebar-button"}
[](#overview-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#overview-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#overview-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button selected"}

Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Synfuel Surge", icon = "glyphicon-random")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$SynSurge$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for synthetic fuels.


<!-- Dividing the page in two columns-->
Row {data-heigth=500}
-----------------------------------------------------------------------

### Per capita Passenger Transport Energy Services Demand
```{r}
plotlist$SynSurge$plot$ESmodecap_pass
```

### Per capita Freight Transport Energy Services Demand
```{r}
plotlist$SynSurge$plot$ESmodecap_frgt
```


Row {data-heigth=500}
-----------------------------------------------------------------------

### Transport Final Energy Demand

```{r}
plotlist$SynSurge$plot$EJfuels
```

### Emissions transport demand

```{r}
plotlist$SynSurge$plot$emidem
```


LDVs {data-icon="fa-car"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#ldvs){class="glyphicon glyphicon-oil sidebar-button selected"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}

<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Conventional Case", icon = "glyphicon-oil")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ConvCase$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Conventional patterns.



<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$ConvCase$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$ConvCase$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$ConvCase$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$ConvCase$plot$vintcomp
```



LDVs FCEV scenario {.hidden data-icon="glyphicon glyphicon-tint"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#ldvs){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button selected"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Hydrogen Hype", icon = "glyphicon-tint")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$HydrHype$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for hydrogen vehicles.

<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$HydrHype$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$HydrHype$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$HydrHype$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$HydrHype$plot$vintcomp
```


LDVs BEV scenario { .hidden data-icon="glyphicon glyphicon-flash"}
===================================== 


Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#ldvs){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button selected"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button"}


<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Electric Era", icon = "glyphicon-flash")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$ElecEra$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for battery electric vehicles.


<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$ElecEra$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$ElecEra$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$ElecEra$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$ElecEra$plot$vintcomp
```


LDVs Synfuel scenario {.hidden data-icon="glyphicon glyphicon-random"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#ldvs){class="glyphicon glyphicon-oil sidebar-button"}
[](#ldvs-fcev-scenario){class="glyphicon glyphicon-tint sidebar-button"}
[](#ldvs-bev-scenario){class="glyphicon glyphicon-flash sidebar-button"}
[](#ldvs-synfuel-scenario){class="glyphicon glyphicon-random sidebar-button selected"}

<!-- Dividing the page in two rows-->
Row {data-height=300}
-----------------------------------------------------------------------

### Transport scenario {data-width=100}
```{r}
valueBox("Synfuel Surge", icon = "glyphicon-random")
```


### Emissions {data-width=100}
```{r}
valueBox(plotlist$SynSurge$emiscen, icon = "fa-cloud")
```


### Scenario description {data-width=200}

Increased preference for synthetic fuels.



<!-- Dividing the page in two rows-->
Row {data-height= 450}
-----------------------------------------------------------------------

### Sales composition {data-width=250}
```{r}
plotlist$SynSurge$plot$salescomp
```


### CO~2~ intensity of new sales {data-width=250}

```{r}
plotlist$SynSurge$plot$CO2km_int_newsales
```


Row {data-height= 450}
-----------------------------------------------------------------------

### Final energy LDVs by fuel
```{r}
plotlist$SynSurge$plot$EJLDV
```


### Fleet composition
```{r}
plotlist$SynSurge$plot$vintcomp
```


<!-- creating information tooltip -->
```{r, results='asis'}
for(i in 1:nrow(helpTooltip_df)){
  cat(helpTooltip(helpTooltip_df[i,]))
}
```


<!-- ADVANCED: using CSS to define the appearance of the side bar --> 

<!-- CSS -->
<style type="text/css">

  .sidebar-button {  /* sidebar size  */
     display: inline-block;
     font-size: 40px;
     height: 80px;
     padding-top: 20px
  }
  
  .sidebar-button, .sidebar-button:hover {
    text-decoration: none;
  }
  
  .sidebar-button.selected, .sidebar-button.selected:hover {
    opacity: 1;
  }
  
  .sidebar-button {
    opacity: 0.7;
  }
  
  .sidebar-button:hover {
    opacity: 0.4;
  }
  
  /*legend*/
  .tooltipContainer {
    padding: 5px;
  }
  
  .tooltipDescription {
    width: fit-content;
    margin: 5px auto;
  }
  
  .legendContainer {
	}

  .legendTable {
    margin:auto;
    text-align: left;
    border-collapse: separate;
    border-spacing: 2px;
	}

  .legendText {
    padding: 4px 20px;
  }

  .legendTable tr:nth-child(odd) {
	  background-color: #1d1e1f; /* Background-color of odd rows */
  }

  .legendTable tr:nth-child(even) {
	  background-color: #32353a; /* Background-color of even rows */
  }

  .square {
    height: 16px; 
    width: 16px; 
    margin: 4px 12px;
  }

  .circle {
    height: 100%; 
    width: 100%; 
    border-radius: 50%; 
    display: inline-block;
  }
  
  .line{
    width: 80%; 
    min-width: 22px;
    border: 1px solid #fff;
    margin: auto;
  }
  
  .units {
    float: right;
    margin: -2px 5px 0 5px;
    color: #b7b7b7;
  }
  
  .infoIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .modalIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .expandIcon {
    float: right;
    margin: 0 5px;
    color: #b7b7b7;
  }
  
  .modalIcon:hover, .infoIcon:hover, .expandIcon:hover {
    color: #7c7c7c;
  }
  
  .unselectable {
    -webkit-touch-callout: none;
    -webkit-user-select: none;
    -khtml-user-select: none;
    -moz-user-select: none;
    -ms-user-select: none;
    user-select: none;
  }

</style>





