<!--
|  (C) 2006-2020 Potsdam Institute for Climate Impact Research (PIK)
|  authors, and contributors see CITATION.cff file. This file is part
|  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
|  AGPL-3.0, you are granted additional permissions described in the
|  REMIND License Exception, version 1.0 (see LICENSE file).
|  Contact: remind@pik-potsdam.de
-->
---
title: "Simple Dashboard"
author: "Renato Rodrigues"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

<!-- We are going to use the flexdashboard library to create a simple dashboard.
     You can find more information in:
     https://rmarkdown.rstudio.com/flexdashboard/
-->


```{r loading_required_libraries, include=FALSE}
  #Loading required libraries
  library(flexdashboard)
  library(ggplot2)
  library(plotly)
  library(magclass)
  library(mip)
```

# Download demonstration data

Before starting the tutorial we need to download the input data we are going to use from PIK's RSE server.

```{r}
download.file("http://rse.pik-potsdam.de/data/example/REMIND_generic_BAU.mif", "REMIND_generic_BAU.mif")

```


```{r reading_data, include=FALSE}
  #Reading a mif file
  data <- read.report("REMIND_generic_BAU.mif",as.list=FALSE)

  # Selecting years until 2100
  data <- data[,getYears(data)<="y2100",]

```



```{r creating_charts, include=FALSE}
  
  plot <- NULL 
  
  # CO2 emissions per sector
  vars <- c("Emi|CO2|Energy|Supply|Non-Elec (Mt CO2/yr)",
            "Emi|CO2|Energy|Supply|Electricity|Gross (Mt CO2/yr)",
            "Emi|CO2|Energy|Demand|Industry|Gross (Mt CO2/yr)",
            "Emi|CO2|FFaI|Industry|Process (Mt CO2/yr)",
            #"Emi|CO2|Industrial Processes (Mt CO2/yr)",
            "Emi|CO2|Buildings|Direct (Mt CO2/yr)",
            "Emi|CO2|Transport|Demand (Mt CO2/yr)",
            "Emi|CO2|Carbon Capture and Storage|Biomass|Neg (Mt CO2/yr)",
            "Emi|CO2|Land-Use Change (Mt CO2/yr)")

  plot$CO2emi <- mipArea(data["EUR",,vars]) +
    theme_minimal() +
    ylab("Mt CO2/yr") 
  
  # CO2 price
  plot$CO2price <- mipLineHistorical(data["EUR",,"Price|Carbon (US$2005/t CO2)"],x_hist=NULL,ylab='US$2005/t CO2') + 
    theme_minimal()
  
  # Electricity mix
  vars <- c("SE|Electricity|Coal|w/ CCS (EJ/yr)", 
            "SE|Electricity|Coal|w/o CCS (EJ/yr)",
            "SE|Electricity|Oil (EJ/yr)",
            "SE|Electricity|Gas|w/ CCS (EJ/yr)", 
            "SE|Electricity|Gas|w/o CCS (EJ/yr)",
            "SE|Electricity|Biomass|w/ CCS (EJ/yr)",  
            "SE|Electricity|Biomass|w/o CCS (EJ/yr)",
            "SE|Electricity|Nuclear (EJ/yr)", 
            "SE|Electricity|Hydrogen (EJ/yr)",
            "SE|Electricity|Solar (EJ/yr)", 
            "SE|Electricity|Wind (EJ/yr)",
            "SE|Electricity|Geothermal (EJ/yr)", 
            "SE|Electricity|Hydro (EJ/yr)")
  
  conversionFactor <- 1/0.0036 # from EJ/yr to TWh
  
  plot$electricityMix <- mipArea(data["EUR",,vars]*conversionFactor, total = F) + 
    theme_minimal() +
    ylab("Electricity Mix (TWh)")

```


<!--############################# -->
<!--#### START OF MENUS CODE #### -->
<!--############################# -->

<!-- ### Creating main emissions menu ### -->

<!--Creating First Page - Emissions Page-->

Emissions {data-icon="glyphicon glyphicon-stats"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#emissions){class="glyphicon glyphicon-stats sidebar-button selected"}
[](#emissions-prices){class="glyphicon glyphicon-eur sidebar-button"}

<!-- Dividing the page in two columns-->
Column
-----------------------------------------------------------------------

<!-- creating a container to show the emissions quantitites-->
### Emissions quantity

```{r}
ggplotly(plot$CO2emi)
```

<!-- Second column-->
Column
-----------------------------------------------------------------------

<!-- creating two additional containers in the second column to show extra information-->

### Emissions quantities empty container 1
```{r}

```


### Emissions quantities empty container 2
```{r}

```


<!-- Creating second page with emissions prices-->

Emissions Prices {.hidden data-icon="glyphicon glyphicon-eur"}
===================================== 

Side Navigation {.sidebar data-width=60}
-------------------------------------

[](#emissions){class="glyphicon glyphicon-stats sidebar-button"}
[](#emissions-prices){class="glyphicon glyphicon-eur sidebar-button selected"}

Column
-----------------------------------------------------------------------

<!-- dividing the page into two containers and showing prices chart in the second one-->

### Emissions prices empty container 1

```{r}
```

### Emissions prices

```{r}
ggplotly(plot$CO2price)
```



<!-- ### Creating electricity sector main menu ### -->

Electricity sector {data-icon="glyphicon glyphicon-scale"}
===================================== 

<!-- dividing the page into two containers and showing the eelectricity sector chart in the first one -->

<!-- creating a container to show the emissions quantitites-->
### Electricity mix empty container 1

```{r}
```

<!-- creating a container to show the emissions quantitites-->
### Electricity mix 

```{r}
ggplotly(plot$electricityMix)
```





<!-- ADVANCED: using CSS to define the appearance of the side bar --> 

<!-- CSS -->
<style type="text/css">

  .sidebar-button {  /* sidebar size  */
     display: inline-block;
     font-size: 40px;
     height: 80px;
     padding-top: 20px
  }
  
  .sidebar-button, .sidebar-button:hover {
    text-decoration: none;
  }
  
  .sidebar-button.selected, .sidebar-button.selected:hover {
    opacity: 1;
  }
  
  .sidebar-button {
    opacity: 0.7;
  }
  
  .sidebar-button:hover {
    opacity: 0.4;
  }

</style>





